Creating optimal conditions for reproducible data analysis in R with `fertile`

### 2019-11-20 fertile.Rmd
revised abstract; #1

---
title: Title here

@@

authors: 
- name: Author 1
  thanks: The authors gratefully acknowledge ...
  affiliation: Department of YYY, University of XXX

- name: Author 2
  affiliation: Department of ZZZ, University of WWW

keywords:
- 3 to 6 keywords
- that do not appear in the title

abstract: |
  The production of reproducible research is key for advancing our scientific knowlege, encouraging transparency, collaboration, and understanding. However, there is no clear consensus on the standards that constitute research reproducibility. In an attempt to build a reproducibility framework in the R community, several packages have been developed to address different aspects of reproducibility, but none are comprehensive. In this paper, we present `fertile`, an R package with an extensive selection of functions designed to thoroughly test reproducibility. Fertile makes creating a reproducibile project as easy as possible for users of all levels of sophistication, providing a simple and comprehensive framework for testing reproducibility in the R community.

  Note: should we add something about the idea of testing the package in a     classroom?

>>>>

---
title: "Creating optimal conditions for reproducible data analysis in R with `fertile`"

@@

authors: 
- name: Audrey Bertin
  thanks: The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the `tidyverse` team. 
  affiliation: Program in Statistical and Data Sciences, Smith College

- name: Benjamin S. Baumer
  affiliation: Program in Statistical and Data Sciences, Smith College

keywords:
- reproducibility
- statistical software
- workflow
- collaboration

abstract: |
  The advancement of scientific knowledge increasingly depends on ensuring that data-driven research is reproducible: that two people with the same data obtain the same results. However, while the necessity of reproducibility is clear, there are significant behavioral and technical challenges that impede its widespread implementation, and no clear consensus on standards of what constitutes reproducibility in published research. We focus on a series of common mistakes programmers make while conducting data science projects in R, primarily through the RStudio integrated development environment. `fertile` is an R package that operates in two modes: proactively (to prevent reproducibility mistakes from happening in the first place), and retroactively (analyzing code that is already written for potential problems). Furthermore, `fertile` is designed to educate the user about why the mistakes are problematic, and how to fix them. We discuss experimental results from testing `fertile` in an introductory data science course.
